Reconstructing Rearrangement Phylogenies of Natural Genomes

### 2023-10-20 docs/manuscript/main.tex
added global constraints

\textbf{For each tree edge $(\A,\B):=\edt\in \tree$ with $\pcmrd(\A,\B) = (\vertices\cup\pseudocaps, \adjacencyedges \cup \extremityedges \cup \selfedges)$:}

\begin{constraints}
\begin{tabular}{lcl}
	\cns & $f_\edt = n_\edt - c_\edt + q_\edt + s_\edt$\\
	\cns & $n_\edt = 0.5 \sum_{e \in \extremityedges} x_{e}$\\
    \cns & $c_\edt = \sum_{v\in \vertices} r^c_{v}$\\
    \cns & $2q_\edt \geq p^{a\trans b}+ p^{ABa} + p^{ABb} - p^{A\trans B} $\\
    \cns & $p^{a\trans b} = \sum_{v \in \vertices}r^{a\trans b}_{v}$\\
    \cns & $p^{A\trans b} = \sum_{v \in \pseudocaps^A} r^{A\trans b}_e$\\
    \cns & $p^{B\trans a} = \sum_{v\in \pseudocaps^B} r^{B\trans a}_e$\\
    \cns & $p^{A\cis a} = \sum_{v \in \pseudocaps^A} r^{A\cis a}_e$\\
    \cns & $p^{B\cis b} = \sum_{e \in \pseudocaps^B} r^{B\cis b}_e$\\
    \cns & $p^{ABa} \geq p^{B\trans a}$\\
    \cns & $p^{ABa} \geq p^{A\cis a}$\\
    \cns & $p^{ABb} \geq p^{B\cis b}$\\
    \cns & $p^{ABb} \geq p^{A\trans b}$\\
    \cns & $p^{A\trans B} = \sum_{v\in \pseudocaps^A} r^{A\trans B}_v$\\
    \cns & $s_\edt = \sum_{v\in\vertices} r^{s}_{v}$ \\
    (\ref{ilp:slmstart}) to (\ref{ilp:slmend})& Shao-Lin-Moret~\cite{SHA-LIN-MOR-2015} constraints& -- see Table~\ref{tab:slmcons}\\
    (\ref{ilp:regvstart}) to (\ref{ilp:regvend})& Reporting for regular vertices& -- see Table~\ref{tab:regv}\\
    (\ref{ilp:pcstart}) to (\ref{ilp:pcend})& Reporting for \gls{pcaps}& -- see Table~\ref{tab:pcaps}\\
    (\ref{ilp:csstart}) to (\ref{ilp:csend})& Reporting circular singletons& --  see Table~\ref{tab:csreport}\\    
\end{tabular}

@@

\begin{constraints}
\caption{Shao-Lin-Moret constraints.} \label{tab:slmcons}
\begin{tabular}{lcl}
 \cns\label{ilp:slmstart} & $\sum_{uv\in \ades} x_{e} = 1 $ & $\forall u\in \vertices$\\
     \cns & $\sum_{uv\in E_{ext} \cup E_{id} } x_{uv}= 1$ & $\forall u\in \vertices$  \\
     \cns & $x_e=x_d$ & for all sibling edges $e,d$\\
     \cns & $y_v + \idx{u}(1-x_{uv}) \geq y_u$ &$\forall uv \in \adjacencyedges\cup \extremityedges$\\
          & $\idx{u}(1-x_{uv})\geq y_u$& $\forall uv \in \selfedges$\\
    \cns\label{ilp:slmend} & $\idx{v}z_v \leq y_v$ & $\forall v\in \vertices\cup\pseudocaps $\\
\end{tabular}
\end{constraints}

>>>>

\textbf{For each ancestral genome $\X \in \tree$ with $\ggraph(\X) = (\vertices, \adjacencyedges)$}

\begin{constraints}
\begin{tabular}{lcl}
    \cns & $\minfam{F} \leq \sum_{v \in F} g_v \leq \maxfam{F}$ & $\forall F \in \families$\\
    \cns & $g_v = g_u$ & for each pair of nodes $(u, v)$ corresponding to head/tail extremity of the same gene\todoDany{improve}\\
    \cns & $g_{v} = x^{\X\A}_{v} = x^{\X\B}_{v} = x^{\X\C}_{v}$& $\forall v \in V$ and genomes $\A$, $\B$, $\C$ adjacent to $\X$ in $\Gamma$\\
    \cns & $\sum_{uv \in \adjacencyedges} a_{uv} = g_u$ & $\forall u \in \vertices$\\
    \cns & $a_{uv} = x^{\X\A}_{uv} = x^{\X\B}_{uv} = x^{\X\C}_{uv}$& $\forall uv \in \adjacencyedges$ and genomes $\A$, $\B$, $\C$ adjacent to $\X$ in $\Gamma$\\
\end{tabular}
\end{constraints}

\medskip
\textbf{For each tree edge $(\A,\B):=\edt\in \tree$ with $\pcmrd(\A,\B) = (\vertices\cup\pseudocaps, \adjacencyedges \cup \extremityedges \cup \selfedges)$:}

\begin{constraints}
\begin{tabular}{lcl}
	\cns & $f_\edt = n_\edt - c_\edt + q_\edt + s_\edt$\\
	\cns & $n_\edt = 0.5 \sum_{e \in \extremityedges} x_{e}$\\
    \cns & $c_\edt = \sum_{v\in \vertices} r^c_{v}$\\
    \cns & $2q_\edt \geq p^{a\trans b}+ p^{ABa} + p^{ABb} - p^{A\trans B} $\\
    \cns & $p^{a\trans b} = \sum_{v \in \vertices}r^{a\trans b}_{v}$\\
    \cns & $p^{A\trans b} = \sum_{v \in \pseudocaps^A} r^{A\trans b}_e$\\
    \cns & $p^{B\trans a} = \sum_{v\in \pseudocaps^B} r^{B\trans a}_e$\\
    \cns & $p^{A\cis a} = \sum_{v \in \pseudocaps^A} r^{A\cis a}_e$\\
    \cns & $p^{B\cis b} = \sum_{e \in \pseudocaps^B} r^{B\cis b}_e$\\
    \cns & $p^{ABa} \geq p^{B\trans a}$\\
    \cns & $p^{ABa} \geq p^{A\cis a}$\\
    \cns & $p^{ABb} \geq p^{B\cis b}$\\
    \cns & $p^{ABb} \geq p^{A\trans b}$\\
    \cns & $p^{A\trans B} = \sum_{v\in \pseudocaps^A} r^{A\trans B}_v$\\
    \cns & $s_\edt = \sum_{v\in\vertices} r^{s}_{v}$ \\
     \cns & $\sum_{uv\in E_{ext} \cup E_{id} } x_{uv}= x_u$ & $\forall u\in \vertices$  \\
    (\ref{ilp:slmstart}) to (\ref{ilp:slmend})& Shao-Lin-Moret~\cite{SHA-LIN-MOR-2015} constraints& -- see Table~\ref{tab:slmcons}\\
    (\ref{ilp:regvstart}) to (\ref{ilp:regvend})& Reporting for regular vertices& -- see Table~\ref{tab:regv}\\
    (\ref{ilp:pcstart}) to (\ref{ilp:pcend})& Reporting for \gls{pcaps}& -- see Table~\ref{tab:pcaps}\\
    (\ref{ilp:csstart}) to (\ref{ilp:csend})& Reporting circular singletons& --  see Table~\ref{tab:csreport}\\    
\end{tabular}

@@

\begin{constraints}
\caption{Shao-Lin-Moret constraints.} \label{tab:slmcons}
\begin{tabular}{lcl}
% \cns\label{ilp:slmstart} & $\sum_{uv\in \ades} x_{e} = 1 $ & $\forall u\in \vertices$\\
    \cns\label{ilp:slmstart} & $x_e=x_d$ & for all sibling edges $e,d$\\
    \cns & $y_v + \idx{u}(1-x_{uv}) \geq y_u$ &$\forall uv \in \adjacencyedges\cup \extremityedges$\\
         & $\idx{u}(1-x_{uv})\geq y_u$& $\forall uv \in \selfedges$\\
    \cns\label{ilp:slmend} & $\idx{v}z_v \leq y_v$ & $\forall v\in \vertices\cup\pseudocaps $\\
\end{tabular}
\end{constraints}
